Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
Couple edits to results writeup

In the median query across a variety of queries and choices of $\alpha$, planning
constituted \planningruntimepercent{} percent of total runtime. In all cases, the optimizer
returned a query plan within \planningmaxtime{} ms, with times roughly constant between levels of $\alpha$.

>>>>

In the median query across a variety of queries and choices of $\alpha$, planning took
\planningmediantime{} ms, 
constituting \planningruntimepercent{} percent of total runtime. In all cases, the optimizer
returned a query plan within \planningmaxtime{} ms, with times similar across values of $\alpha$.
